### 2023-10-29 generalExploration.Rmd
Random split for #4

    ## Fission
    overloaded=initcomus$size>Th
    if(sum(overloaded)>0){
        for(split in which(overloaded))
            print(paste("community",split,"with size",initcomus$size[split]))
        #        for(split in which(overloaded))

>>>>

    ## Fission
    overloaded=initcomus$size>Th
    if(sum(overloaded)>0){
        listcomu=sapply(population,"[[","community")
        for(split in which(overloaded)){
            print(paste("community",split,"with size",initcomus$size[split]))
            tosplit= (listcomu == split)
            initcomus
            moving=sample(names(population)[tosplit],initcomus$size[split]/2)
        }
